\section{Introduction}\label{sec:introduction}

Decentralized blockchains face a number of pressing challenges.
Scalability, interoperability, and governance are only a few of the concepts
that researchers have been working on during the decade since 2009, when
Bitcoin~\cite{nakamoto2008bitcoin} first launched. Nevertheless, technical
issues, although immensely interesting, are not the only challenges that such
systems face. A common theme that arises in discussions and articles regarding
the future of decentralized blockchains is \emph{adoption}.

Mainstream adoption has been almost ubiquitously hailed as the way for
blockchain systems to mature and, potentially, appreciate in value. Indeed, as
more people build on and use decentralized ledgers, it is expected that more
research opportunities will arise, while helping researchers and entrepreneurs
alike. Eventually, adoption should allow the scientific knowledge and
technological standards of distributed ledgers to mature faster and better.

A core element regarding adoption of every new technology, like blockchains, is
compliance with the existing regulatory frameworks. As early as 2010, questions
on how, or even if, Bitcoin can be a legal assets have sparked a heated
discussion\footnote{One of the first such discussions is available at Eric
Roberts' webpage:
\url{https://cs.stanford.edu/people/eroberts/courses/cs181/projects/2010-11/Bitcoins/should-bitcoin-be-legal.html}}.
However, due to the fact that the legal framework has been trailing the
technological advancements, in more than one occasions established
organizations have been hesitant or abstained from using the new blockchain
technology\footnote{A primary example is the Electronic Frontier Foundation's
step back in accepting Bitcoin as a donation option in 2011, due to ``complex
legal issues'', as explained in the following blog post:
\url{https://www.eff.org/deeplinks/2011/06/eff-and-bitcoin}}. It is thus clear
that, in order for --- decentralized --- blockchains to be widely used, proper
tools should be developed that will allow enterprises in this space to comply
with the changes in the legal framework, while retaining the much needed
properties that technology has to offer, such as privacy.

Crypto-assets, and especially cryptocurrency exchanges, have drawn a lot of
attention from the tax authorities recently, especially after the surge in
Bitcoin's price during 2017. Additionally, exchanges, being the primary
platforms for exchanging cryptocurrency and shaping the market's prices, have
been on put on the spot by authorities across the globe. Primary examples are
the U.S. Securities and Exchange Commission, which as of 2018 require exchanges
to register with it~\cite{securities2018statement}, as well as the Australian
tax office, which applies the trading stock rules on
exchanges~\cite{tax2019statement}.

In this paper we explore a mechanism for the taxation of cryptocurrency
exchanges. First, we explore the necessary properties that such mechanism
should offer, in order to comply with the information needs of the taxation
authority. Our design aims to maintain the best level of privacy possible, both
for the exchanges and their users, as well as minimize the level of trust that
needs to be assumed of the taxation authority. Therefore, we next establishing
the core limitations of every such taxation mechanism.

Second, our paper introduces a taxation design, which is based on
Provisions~\cite{CCS:DBBCB15}. Provisions is a proof of solvency mechanism for
Bitcoin exchanges, which we extend by utilizing well-known cryptographic
primitives, specifically Schnorr's protocol for proof of knowledge. Our scheme
allows exchanges to declare the assets that they manage, without the need to
disclose any additional information. More importantly, we describe how a
taxation authority can use our scheme in order to identify whether an exchange
fails to declare some or all of its assets.
%
% Finally, we extend the Provisions
% implementation\footnote{\url{https://github.com/bbuenz/provisions}} with our
% taxation mechanism.  Our benchmarks show that the extension is lightweight,
% especially compared to the other pieces of Provisions, and thus is suitable for
% widespread usage by existing exchanges.\comment{add numbers}
